---
title: "Getting Started with dkw"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with dkw}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

## Introduction

The `dkw` package provides tools for computing confidence bounds on individual treatment effect distributions using DKW (Dvoretzky-Kiefer-Wolfowitz) and Makarov bounds.

```{r load-package}
library(dkw)
```

## Quick Example: Computing Makarov Bounds

Given treatment and control group outcomes, compute bounds on the treatment effect distribution:

```{r basic-example}
set.seed(123)

# Simulate treatment and control outcomes
Y1 <- rnorm(100, mean = 1.5, sd = 1)  # Treatment group
Y0 <- rnorm(100, mean = 0, sd = 1)    # Control group

# Compute Makarov bounds (90% confidence)
result <- makarov_bounds(Y1, Y0, alpha = 0.1)

# View structure
str(result, max.level = 1)
```

## Visualizing the Bounds

```{r plot-bounds}
# Plot the bounds
plot(result$bounds_matrix[, "t"], result$bounds_matrix[, "upper"],
     type = "l", col = "red", ylim = c(0, 1),
     xlab = "Treatment Effect", ylab = "CDF",
     main = "Makarov Bounds on Treatment Effect Distribution")
lines(result$bounds_matrix[, "t"], result$bounds_matrix[, "lower"], col = "blue")
legend("bottomright", c("Upper Bound", "Lower Bound"),
       col = c("red", "blue"), lty = 1)
```

## Extracting Quantile Confidence Intervals

Get lower confidence limits for specific quantiles:

```{r quantile-ci}
# Extract CIs for deciles
ci <- extract_quantile_ci(result, quantiles = seq(0.1, 1, by = 0.1))
print(ci)
```

## Interpretation

- The **lower bound** (blue) gives the minimum possible CDF value at each treatment effect
- The **upper bound** (red) gives the maximum possible CDF value
- For quantile q, if `lower_ci > 0`, we can conclude that at least (1-q) fraction of units have positive treatment effects
