---
title: "Makarov Bounds for Treatment Effects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Makarov Bounds for Treatment Effects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

## The Makarov Inequality

Makarov bounds provide sharp bounds on the CDF of the sum (or difference) of two random variables given only their marginal distributions.

For treatment effects $\tau_i = Y_i(1) - Y_i(0)$:

$$L(t) = \sup_x \max\left(0, F_1(x) - F_0(x-t)\right)$$
$$U(t) = \inf_x \min\left(1, F_1(x) - F_0(x-t) + 1\right)$$

```{r load}
library(dkw)
```

## Computing Makarov Bounds

```{r basic-makarov}
set.seed(123)

# Simulate experiment
Y1 <- rnorm(150, mean = 2, sd = 1)    # Treatment outcomes
Y0 <- rnorm(150, mean = 0, sd = 1)    # Control outcomes

# Compute Makarov bounds
result <- makarov_bounds(Y1, Y0, alpha = 0.1)

# Structure of result
names(result)
dim(result$bounds_matrix)
```

## Visualizing the Bounds

```{r plot-makarov}
bounds <- result$bounds_matrix

plot(bounds[, "t"], bounds[, "upper"],
     type = "l", col = "red", lwd = 2,
     ylim = c(0, 1),
     xlab = "Treatment Effect (t)",
     ylab = "CDF Bounds",
     main = "Makarov Bounds on Treatment Effect Distribution")

lines(bounds[, "t"], bounds[, "lower"], col = "blue", lwd = 2)

# Add reference line at t = 0
abline(v = 0, lty = 2, col = "gray")

legend("bottomright",
       c("Upper Bound", "Lower Bound"),
       col = c("red", "blue"), lwd = 2)
```

## With True Treatment Effects (Simulation)

When we simulate data, we can compare bounds to the true CDF:

```{r with-true}
set.seed(42)

# Generate with known potential outcomes
data <- generate_potential_outcomes(m = 300, tau = 1.5, rho = 0.4)

# Extract observed outcomes
Y1 <- data$Y[data$Z == 1]
Y0 <- data$Y[data$Z == 0]

# Compute bounds
result <- makarov_bounds(Y1, Y0, alpha = 0.1)
bounds <- result$bounds_matrix

# Plot with true CDF
plot(ecdf(data$tau), main = "Makarov Bounds vs True CDF",
     xlab = "Treatment Effect", ylab = "CDF")

lines(bounds[, "t"], bounds[, "lower"], col = "blue", lwd = 2)
lines(bounds[, "t"], bounds[, "upper"], col = "red", lwd = 2)

legend("bottomright",
       c("True CDF", "Lower Bound", "Upper Bound"),
       col = c("black", "blue", "red"), lwd = c(1, 2, 2))
```

## Quantile Confidence Intervals

Extract confidence intervals for specific quantiles:

```{r quantile-ci}
# Get CIs for specific quantiles
ci <- extract_quantile_ci(result, quantiles = c(0.1, 0.25, 0.5, 0.75, 0.9))
print(ci)

# Compare to true quantiles
true_q <- quantile(data$tau, ci$quantile)

comparison <- data.frame(
  quantile = ci$quantile,
  lower_ci = round(ci$lower_ci, 3),
  true_value = round(true_q, 3),
  covered = true_q >= ci$lower_ci
)
print(comparison)
```

## Effect of Sample Size

```{r sample-size, fig.height=4}
par(mfrow = c(1, 3))

for (m in c(50, 200, 500)) {
  d <- generate_potential_outcomes(m = m, tau = 2, rho = 0.3)
  Y1 <- d$Y[d$Z == 1]
  Y0 <- d$Y[d$Z == 0]

  res <- makarov_bounds(Y1, Y0, alpha = 0.1)
  b <- res$bounds_matrix

  plot(ecdf(d$tau), main = paste("m =", m),
       xlab = "Treatment Effect", ylab = "CDF")
  lines(b[, "t"], b[, "lower"], col = "blue", lwd = 2)
  lines(b[, "t"], b[, "upper"], col = "red", lwd = 2)
}
```

## Effect of Correlation

Higher correlation = looser bounds:

```{r correlation, fig.height=4}
par(mfrow = c(1, 3))

for (rho in c(0.1, 0.5, 0.9)) {
  d <- generate_potential_outcomes(m = 200, tau = 2, rho = rho)
  Y1 <- d$Y[d$Z == 1]
  Y0 <- d$Y[d$Z == 0]

  res <- makarov_bounds(Y1, Y0, alpha = 0.1)
  b <- res$bounds_matrix

  plot(ecdf(d$tau), main = paste("rho =", rho),
       xlab = "Treatment Effect", ylab = "CDF")
  lines(b[, "t"], b[, "lower"], col = "blue", lwd = 2)
  lines(b[, "t"], b[, "upper"], col = "red", lwd = 2)
}
```
